#####
**Data frame basic**

```{r}
state.x77
```
```{r}
USPersonalExpenditure
```
```{r}
women
```
```{r}
data()
```
```{r}
WorldPhones
```
```{r}
head(state.x77)
```
```{r}
tail(state.x77)
```
```{r}
str(state.x77)
```
```{r}
summary(state.x77)
```
```{r}
days <- c('Mon', 'Tue', 'Wed', 'Thu', 'Fri')
temp <- c(22.2, 21, 23, 24.3, 25)
rain <- c(T, T, F, F, T)

df <- data.frame(days, temp, rain)
df
```
```{r}
str(df)
```
```{r}
summary(df)
```
#####
**Indexing and selection**
```{r}
df
```
```{r}
df[1, ]
```
```{r}
df[, 1]
```
```{r}
df[, 'rain']
```
```{r}
df[1:5, c('days', 'temp')]
```
```{r}
df$days
```
```{r}
df$temp
```
```{r}
df['days']
```
```{r}
subset(df, subset=(rain == TRUE))
```
```{r}
subset(df, subset=(temp > 23))
```
```{r}
sorted.temp <- order(df['temp'])
sorted.temp
```
```{r}
df[sorted.temp, ]
```
```{r}
desc.temp <- order(-df['temp'])
desc.temp
```
```{r}
df[desc.temp, ]
```
#####
**Data frame operations part 1**
Creating data frame

```{r}
empty <- data.frame()
empty
```

```{r}
c1 <- 1:10
c2 <- letters[1:10]

df <- data.frame(col.name.1=c1, col.name.2=c2)
df
```
Importing and exporting data frame

```{r}
write.csv(df, file='./datasets/saved_df.csv')
df2 <- read.csv('./datasets/saved_df.csv')
df2
```
Getting information about the data frame

```{r}
df
```

```{r}
nrow(df)
```
```{r}
ncol(df)
```
```{r}
colnames(df)
```
```{r}
rownames(df)
```
```{r}
str(df)
```
```{r}
summary(df)
```

Referencing cells

```{r}
df
```
```{r}
df[[5, 2]]
```
```{r}
df[[5, 'col.name.2']]
```
```{r}
df[[2, 'col.name.1']] <- 9999
```
```{r}
df
```

Referencing rows

```{r}
df[1, ]
```

Referencing columns

```{r}
mtcars
```
```{r}
mtcars['mpg']
```

```{r}
mtcars$'mpg'
```
```{r}
mtcars[, 'mpg']
```
```{r}
mtcars[, 1]
```
```{r}
mtcars[['mpg']]
```
```{r}

```
```{r}
mtcars[c('mpg', 'cyl')]
```
#####
**Data frame operations part 2**
Adding rows and columns

```{r}
df2 <- data.frame(col.name.1=2000, col.name.2='new')
df2
```
```{r}
dfnew <- rbind(df, df2)
dfnew
```
```{r}
df
```
```{r}
df$'newcol' <- 2*df$'col.name.1'
df
```
```{r}
df$'newcol.copy' <- df$'newcol'
df
```
```{r}
df[, 'newcol.copy2'] <- df$'newcol'
df
```

Setting column names

```{r}
colnames(df)
```
```{r}
colnames(df) <- c('1', '2', '3', '4', '5')
df
```
```{r}
colnames(df)[1] <- 'new.col.name'
df
```

Selecting multiple rows and columns

```{r}
df[1:10, ]
```
```{r}
df[1:3, ]
```
```{r}
head(df)
```
```{r}
head(df, 7)
```
```{r}
df[-2, ]
```
```{r}
head(mtcars)
```
```{r}
mtcars[mtcars$'mpg' > 20, ]
```
```{r}
mtcars[(mtcars$'mpg' > 20) & (mtcars$'cyl' == 6), ]
```
```{r}
mtcars[(mtcars$'mpg' > 20) | (mtcars$'cyl' == 6), ]
```
```{r}
mtcars[(mtcars$'mpg' > 20) & (mtcars$'cyl' == 6), c('mpg', 'cyl', 'hp')]
```
```{r}
subset(mtcars, (mpg > 20) & (cyl == 6))
```
```{r}
mtcars[, c(1, 2, 3)]
```
```{r}
mtcars[, c('mpg', 'cyl', 'disp')]
```

Dealing with missing data

```{r}
any(is.na(mtcars))
```
```{r}
any(is.na(mtcars$'mpg'))
```
```{r}
df
```
```{r}
df[is.na(df)] <- 0
```
```{r}
mtcars$'mpg'[is.na(mtcars$'mpg')] <- mean(mtcars$'mpg')
```
